---
title: "Election Data"
author: "Sarah Brashear"
date: "3/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(rstanarm)
```


```{r}
x <- read_csv(file = "raw_data/results.csv", skip = 1) %>%
  select(CD, Biden, Trump) %>%
  mutate(winner = ifelse(Biden > Trump, 1, 0))

results <- x %>%
  select(CD:Romney)
```

What percentage of Congressional districts did Biden win? 
How would you estimate that if I just showed you the results from 50 units?

## One way to solve

```{r}

bidencount <- results %>%
  select(CD, Biden, Trump) %>%
  mutate(winner = ifelse(Biden > Trump, 1, 0)) %>%
  summarize(bidencount = sum(winner == 1)) 


trumpcount <- results %>%
  select(CD, Biden, Trump) %>%
  mutate(winner = ifelse(Biden > Trump, 1, 0)) %>%
  summarize(trumpcount = sum(winner == 1))

totalcount <- bidencount + trumpcount

biden_perc <- bidencount/totalcount

```

## A different way

```{r}
bidenperc <- results %>%
  select(CD, Biden, Trump) %>%
  mutate(winner = ifelse(Biden > Trump, 1, 0)) %>%
  summarize(bidencount = sum(winner == 1) / n())

```

## Taking samples of 50

```{r, random_sample}

small <- x %>%
  slice_sample(n = 50)

```


```{r, first_50}
top50 <- x %>%
  slice(1:50)
```

Population & representativeness 

First 50 - the A name districts happen to be more likely to be Republican
think: Alabama, Arkansas, Arizona

Every 9th - not perfectly random, but does span more different states than 
just the first 50??

Random 50 - more representative, 50 out of 435 is a pretty large chunk 



Our population - all 435 US Congressional districts
units - each Congressional district


```{r}

fit_1 <- stan_glm(formula = winner ~ 1, 
                  data = small,
                  family = binomial,
                  refresh = 0,
                  seed = 2021)

```





